%!TEX TS-program = xelatex
\documentclass[avery5371,grid,frame]{flashcards}
\input{tex/page_headings.tex}
\input{tex/arabic_common.tex}
\title{UC Class Vocab}
\newcommand{\myurl}{\url{http://berkeleyarabic.github.io/flashcards/}}
\begin{document}
\cardfrontstyle{headings}
\cardfrontfoot{}
\begin{flashcard}{\LARGE I have a question}
\LARGE \ta{عِندي سُؤال}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Do you have a question?}
\LARGE \ta{هل عندَكم سُؤال؟}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE answer, reply}
\LARGE \ta{إجابة ج -ات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE question}
\LARGE \begin{tabularx}{\textwidth}{>{\raggedright}X>{\raggedleft}X}
suʾāl pl. ʾasʾila & \ta{سُؤال ج أسئِلة} \\
\end{tabularx}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE How do we say ... in Arabic?}
\LARGE \ta{كَيف نَقول...بالعربية؟}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE to say, tell}
\LARGE \ta{قال،يَقول،القَول}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE What does ... mean in English?}
\LARGE \ta{ما معنى بالإنجايزية؟}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE ... means ... in English.}
\LARGE \ta{...بِمعنى...بالﻹنجايزية.}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE meaning, import, sense}
\LARGE \ta{مَعنى ج مَعاني}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE please}
\LARGE \ta{مِن فضلكَ/فضلكِ/فضلكم}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE If you please}
\LARGE \ta{لَو سَمَحتَ/لَو سَمَحتِ/لَو سَمَحتُم...}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE one more time}
\LARGE \ta{مَرّة أُخرى}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE a second time}
\LARGE \ta{مَرّة ثانية}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE a time, instance, occurrence}
\LARGE \ta{مَرَّة ج مَرّات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Come on!}
\LARGE \ta{ياللا!/هَيَا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE come!}
\LARGE \begin{tabularx}{\textwidth}{>{\raggedright}X>{\raggedleft}X}
taʿāla/taʿālay/taʿālaw & \ta{تَعالَى/تَعالي/تَعالوا} \\
\end{tabularx}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Come to the board}
\LARGE \ta{تعالى إلى السبورة}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Board (blackboard, whiteboard, etc.)}
\LARGE \ta{سَبورة ج -ات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE I would like you to write / read / listen / sit / get up / ask}
\LARGE \ta{أريدُكم أنْ تكتبوا.../تقرأوا..../تسمعوا..../تجلسوا/تقوموا..../تسألوا....}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE I want ... from you}
\LARGE \ta{أريد منكم...}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Write!}
\LARGE \ta{اُكتُب/اُكتبي/اُكتُبوا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Read!}
\LARGE \ta{اِقرأ/اِقرأي/أقرأوا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Listen!}
\LARGE \ta{اِسمَع/اِسمَعي/اِسمَعوا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Sit!}
\LARGE \ta{اِجلِس/اِجلِسي/اِجلِسوا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Get up {[}out of your seats{]}!}
\LARGE \ta{قُم/قُومي/قُوموا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Ask!}
\LARGE \ta{اِسأل/اِسألي/اِسألوا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Ask your classmates}
\LARGE \ta{اِسألوا زملاءكم}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE orally}
\LARGE \ta{شَفَوي/شَفَوياً/شَفَهيً/شَفَهياً}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE This is an oral exercise ... Don't write!}
\LARGE \ta{‏هذا التمرين شفوي...لا تكتبوا!‏}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE This is an oral exercise ... Don't write!}
\LARGE \ta{هذا التمرين شفوي...لا تكتبوا!}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE practice, exercise}
\LARGE \ta{تَمرين ج تمارين/تمرينات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE in a loud voice}
\LARGE \ta{في صوت عالٍ}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE voice}
\LARGE \ta{صَوت ج أَصوات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE with a classmate / with a new classmate}
\LARGE \ta{مع زميا أو زميلة/مع زميل جديد أو زميلة جديدة}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE classmate, colleague, fellow}
\LARGE \ta{زَميل ج زُمَلاء}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE in groups of two / three}
\LARGE \ta{في مجموعات اثنين/ثلاثة}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE group, collection}
\LARGE \ta{مجموعة ج مجموعات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE together}
\LARGE \ta{معاً = مع بَعض}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE some}
\LARGE \ta{بَعض}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Let's talk/sit together}
\LARGE \ta{ياللا نتكلم/نجلس مع بعض}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Let's read the instructions together}
\LARGE \ta{ياللا نقرأ الإرشادات مع بعض}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE instructions}
\LARGE \ta{إرشادات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE worksheet}
\LARGE \ta{ورقة عمل}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE cards}
\LARGE \ta{بِطاقة ج -ات/كارت ج كُروت}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE This is a competition!}
\LARGE \ta{هده مُسابَقة!}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE competition}
\LARGE \ta{مُسابَقة ج -ات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE This is a game}
\LARGE \ta{هذه لُعبة}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE game; trick}
\LARGE \ta{لُعبة ج أُلعاب}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE quickly}
\LARGE \ta{بِسُرعة}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE correct}
\LARGE \ta{صَحيح}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE wrong, mistaken}
\LARGE \ta{خَطَا}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE point (in a game)}
\LARGE \ta{نُقطة ج نِقاط}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE tie in a game (same scores)}
\LARGE \ta{تَعادُل}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE grade, point}
\LARGE \ta{دَرَجة ج دَرَجات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE scheme, project}
\LARGE \ta{مَشروع ج مَشاريع/مسروعات}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE done!; enough!; stop it!}
\LARGE \ta{خَلاص}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE Are you done?}
\LARGE \ta{هل اِنتَهَيتُم/خَلَّصتُم؟}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE finished with, over, complete}
\LARGE \ta{اِنتَهَى من،يَنتَهي من،الاِنتِهاء من}
\end{flashcard}
\cardfrontfoot{}
\begin{flashcard}{\LARGE to end}
\LARGE \ta{خَلَّص،يُخَلَّص}
\end{flashcard}
\end{document}
